\plaintitle

### 2017-04-26 statistical-quorum.tex
Exposing related work TODOs.

% threshold and quorum at https://www.publications.parliament.uk/pa/ld200910/ldselect/ldconst/99/99.pdf
% how does some claim that quorum are in fact bad, and counter democratic, but do not offer a solution how to evaluate them

% repeat references from "There have been many improvements proposed to this basic form and various analysis made."?

% voting auditing

% delegation as way to increase legitimacy

>>>>

\todo[inline]{Repeat references from "There have been many improvements proposed to this basic form and various analysis made."?}

\todo[inline]{Threshold and quorum at \url{https://www.publications.parliament.uk/pa/ld200910/ldselect/ldconst/99/99.pdf}.
How do some claim that quorum are in fact bad, and counter democratic, but do not offer a solution how to evaluate decisions.}

\todo[inline]{Voting auditing work.}

\todo[inline]{Delegation as way to increase legitimacy, Liquid Democracy, etc.}
